---
title: "Vizualising NZ rivers with `eeda`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vizualising NZ rivers with `eeda`}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(eval = TRUE, warning = FALSE, message = FALSE, cache = TRUE)
knitr::read_chunk("viz.R")
```

```{r,libs,echo = TRUE}
```

```{r,quiet,echo = FALSE}
```

Download and return a `SpatialLinesDataFrame` of NZ rivers. If `plot = TRUE` then a plot is also printed.

```{r,demo,echo = TRUE,fig.width = 5, fig.height = 8}
```

Search for particular river name and return a `SpatialLinesDataFrame`. If `plot = TRUE` then a plot is also printed.

```{r,waikato, echo = TRUE,fig.width = 5, fig.height = 8}
```

Alternitevely return all rivers in a province. Note that if the argument `network = TRUE` then all connected river segments are returned (including those outwith the specified province). 

```{r,canter,echo = TRUE}
```

Note that `get_nz_river` returns a `SpatialLinesDataFrame`; if you wish to deal with a simple features object then you can use `st_as_sf()` from the `sf` package to transform.

```{r,sf,echo = TRUE,fig.width = 5, fig.height = 5}
```
